Incoherent Deep Virtual Compton Scattering off $^4$He using CLAS spectrometer

### 2017-03-23 eg6-letters/incoherent/incoherent_prl.tex
update the incoherent channel investigation regarading t, t' and update the incoherent prl

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

@@

\bibitem{Vadim_priv}
Private communications with V.~Guzey based on: 
V.~Guzey, Phys.\ Rev.\ C {\bf 78}, 025211 (2008).

@@

\bibitem{Guidal_priv}
Private communications with M.~Guidal based on: 
M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 
Phys.\ Rev.\ D {\bf 72}, 054013 (2005).

@@

\bibitem{GonzalezHernandez:2012jv}
Private communications with S.~Liuti based on: 
J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).

>>>>

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
\cite{Airapetian}, the colored curves represent theoretical calculations from 
\cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{Airapetian} 
   results.  The blue and red curves are from an on-shell calculations from S.  
   Liuti and K.  Taneja \cite{simonetta_2}. The solid and dashed black curves 
are from the off-shell calculations \cite{Guzey:2008fe}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

@@

%\cite{Guzey:2008fe}
\bibitem{Guzey:2008fe} 
   V.~Guzey, A.~W.~Thomas and K.~Tsushima,
  Phys.\ Lett.\ B {\bf 673}, 9 (2009)

@@
